---
title: ""  
author: "`r rworkflows::use_badges(add_actions=c('rworkflows','rworkflows_static','rworkflows_dev'), add_cran_release = TRUE, add_cran_checks = TRUE, add_cran_download_month=TRUE, add_cran_download_total=TRUE, add_codecov_graphs='icicle', hex_height=350, add_doi='https://doi.org/10.5281/zenodo.10048573')`" 
date: "<h4>README updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  github_document
---

```{r setup, include=FALSE}
pkg <- read.dcf("DESCRIPTION", fields = "Package")[1]
```
## 📘 Citation 

If you use of reference the ``r pkg`` suite, please cite: 

<!-- Modify this by editing the file: inst/CITATION  -->
> `r utils::citation(pkg)$textVersion`

## ℹ Intro

### 📖 Background

`rworkflows` is a suite of tools to make it easy for R developers to implement
reproducible best practices on GitHub. 

It includes three main components:  
1. [**`templateR` template**](https://github.com/neurogenomics/templateR): a `CRAN`/`Bioc`-compatible R package template that automatically generates essential documentation using package metadata.  
2. [**`rworkflows` R package**](https://github.com/neurogenomics/rworkflows/blob/master/DESCRIPTION): a lightweight `CRAN` package to automatically 
set up short, customisable workflows that trigger the `rworkflows` action.  
3. [**`rworkflows` action**](https://github.com/neurogenomics/rworkflows/blob/master/action.yml): an open-source action available on the [GitHub Actions  Marketplace](https://github.com/marketplace/actions/rworkflows). 

### ⚙️ `rworkflows` action steps 

[**GitHub Actions**](https://docs.github.com/en/actions) 
are a powerful way to automatically launch workflows 
every time you push changes to a GitHub repository. 
This is a form of [**Continuous Integration/Deployment (CI/CD)**](https://docs.github.com/en/actions/automating-builds-and-tests/about-continuous-integration),
which helps ensure that your code is always working as expected 
(without having to manually check each time).

Here, we have designed a robust, reusable, and flexible **action** 
specifically for the development of R packages. 
We also provide an R function to automatically generate a **workflow file** that 
calls the `rworkflows` composite action:

Currently, `rworkflows` **action** can perform the following tasks
(with options to enable/disable/modify each step):  

1. 🐳 Builds a Docker container to run subsequent steps within. 
2. 🐍 Builds and/or activates a custom `conda` environment.
3. 🛠️ Installs system dependencies
4. 🛠️ Installs LaTeX dependencies.
5. 🛠 Installs R dependencies.
6. ✅ Builds and checks your R package (with [**CRAN**](https://cran.r-project.org/)
and/or [**Bioconductor**](https://bioconductor.org/) checks).  
7. 📋 Runs [unit tests](https://testthat.r-lib.org/).  
8. 📋 Runs [code coverage tests](https://covr.r-lib.org/) and uploads the results 
to [**Codecov**](https://about.codecov.io/).  
9. 🚀 (Re)builds and launches a documentation website for your R package.  
10. 🐳 Pushes a [**Docker**](https://www.docker.com/) container (with [**Rstudio**](https://posit.co/) and all dependencies pre-installed) to 
your choice of container registry (e.g. [**GitHub Container Registry**](https://docs.github.com/en/packages/working-with-a-github-packages-registry/working-with-the-container-registry),  [**DockerHub**](https://hub.docker.com/)). 
11. 🔭 Generates [workflow telemetry](https://github.com/runforesight/workflow-telemetry-action) report.  
12. 🎖 Updates relevant badges added to your README 
with `rworkflows::use_badges()`.

Importantly, this **workflow** is designed to work with any R package out-of-the-box.
This means you won't have to manually edit any yaml files,
just run the `rworkflows::use_workflow()` function 
and you're ready to go within seconds!

> **🙏 Acknowledgements**: `rworkflows` uses, was inspired by, and benefits from the work of [many other projects](#acknowledgments), especially: [`biocthis`](https://github.com/lcolladotor/biocthis), [`usethis`](https://github.com/r-lib/usethis), [`actions/`](https://github.com/actions), [`r-lib/actions`](https://github.com/r-lib/actions), [`bioc-actions`](https://github.com/grimbough/bioc-actions), [`JamesIves/github-pages-deploy-action`](https://github.com/JamesIves/github-pages-deploy-action), [`docker/build-push-action`](https://github.com/docker/build-push-action), [`bioconductor_docker`](https://github.com/Bioconductor/bioconductor_docker).  
 
## ⏩ Quickstart

Install and create the workflow in your R package's project folder.

In R (only need to do once per repository):
```R
### 1. Install stable CRAN release
if(!require("rworkflows")) install.packages("rworkflows")
### Or, install latest development version
# if(!require("rworkflows")) remotes::install_github("neurogenomics/rworkflows")

### 2. Create workflow file
path <- rworkflows::use_workflow()
```
Then, in the Terminal:  
```bash
### 3. Push to GitHub
git add .
git commit -m "Added rworkflows" # Arbitrary commit message
git push
```

Now you can let everything run on GitHub automatically!
You can check the status of your workflow by clicking on the [*Actions* tab](https://github.com/neurogenomics/rworkflows/actions)
in your GitHub repo.

### 🤫 Special commit messages 
Including special keywords in your commit message will have a certain effect:  
- `"[skip ci]"`: will skip running the workflow on this push.  
- `"[nodocker]"`: will skip any Docker registry steps.  
- `"[noncache]"`: will not use any cached installations or files.  

For example: `git commit -m "Update README [skip ci]"` will skip running any GitHub Actions.

### 🔐 GitHub Secrets
To use certain features of `rworkflows`, you may need to set up one or more
[GitHub Secrets](https://docs.github.com/en/actions/security-guides/encrypted-secrets):

* `PAT_GITHUB` [Optional]: Can grant access to private
    repos on GitHub Actions. You can generate your very own Personal
    Authentication Token with `usethis::create_github_token()`. [See more](https://docs.github.com/en/authentication/keeping-your-account-and-data-secure/creating-a-personal-access-token).   
* `DOCKER_TOKEN` [Optional]: Allows GitHub Actions to push to a
    [DockerHub](https://hub.docker.com) account. [See more](https://docs.docker.com/security/for-developers/access-tokens/).  
* `CODECOV_TOKEN` [Optional]: Bypasses issues that occasionally arise from GitHub API limits. [See more](https://docs.codecov.com/reference/overview).
* `GitHub Variables` [Optional]: These are default variables that are automatically set by GitHub Actions. [See more](https://docs.github.com/en/actions/reference/environment-variables#default-environment-variables).

## 📚 Documentation

### [🧑‍🎓 Vignettes](https://neurogenomics.github.io/rworkflows/articles/)

- [📖 **Get started**](https://neurogenomics.github.io/rworkflows/articles/rworkflows.html): Introductory vignette for using `rworkflows`.  
- [🐳 **Docker/Singularity**](https://neurogenomics.github.io/rworkflows/articles/docker): Copy-and-paste instructions for creating a **Docker** or **Singularity** container with the `rworkflows` R package pre-installed.  
- [🕸️ **Dependency graph**](https://neurogenomics.github.io/rworkflows/articles/depgraph):  Interactive graph showing all the GitHub repos that currently use 
the `rworkflows` action.  

### [🎥 Videos](https://www.youtube.com/@NeurogenomicsLab)

- [🤠 **rworkflows: taming the Wild West of R packages**](https://youtu.be/nLIG2prEmCg): Talk on the background, motivation, and utility of `rworkflows`.  
- [🌊 **Getting into the flow with rworkflows: an introductory tutorial**](https://youtu.be/vcpMsil3EAU): Step-by-step tutorial showing how to use `rworkflows` in an R package.  

## 🙏 Acknowledgments
`rworkflows` builds upon the work of many others, especially the following:

- [`biocthis`](https://github.com/lcolladotor/biocthis): This workflow is largely inspired by the workflow generated by the 
[`use_bioc_github_action()`](https://lcolladotor.github.io/biocthis/articles/biocthis.html) function within the [`biothis`]( https://www.bioconductor.org/packages/release/bioc/html/biocthis.html) 
package, developed by @lcolladotor. Key changes in `rworkflows` 
  - Uses dynamic variables to specify R/Bioconductor versions 
(e.g. `r: "latest"`) and the name of your R package, as opposed to static 
names that are likely to become outdated (e.g. `r: "4.0.1"`).  
  - Additional error handling and dependencies checks.  
  - Re-renders `README.Rmd` before rebuilding the documentation website.  
  - Conda support
  - Ability to change registry  
- [`usethis`](https://github.com/r-lib/usethis): `biocthis` was in turn inspired by `usethis`.  
- [`actions/`](https://github.com/actions): A general set of **GitHub Actions** maintained by the core GitHub team.  
- [`r-lib/actions`](https://github.com/r-lib/actions): A set of **GitHub Actions** for R development maintained by the Rstudio/Posit team.  
- [`bioc-actions`](https://github.com/grimbough/bioc-actions)
[Bioconductor](https://www.bioconductor.org/)-oriented **GitHub Actions** created by @grimbough.  
- [`JamesIves/github-pages-deploy-action`](https://github.com/JamesIves/github-pages-deploy-action): Builds and deploys the **GitHub Pages** documentation website
in the `rworkflows` GHA workflows.  
- [`docker/build-push-action`](https://github.com/docker/build-push-action): A set of **GitHub Actions** for building/pushing **Docker** containers.  
- [`bioconductor_docker`](https://github.com/Bioconductor/bioconductor_docker): Uses the official [`bioconductor/bioconductor_docker`](https://github.com/Bioconductor/bioconductor_docker) **Docker** container.  
  - **Note**: Whenever a new version of Bioconductor is released, the `bioconductor/bioconductor_docker` container will often lag behind the actual. Bioconductor releases for up to several days, due to the time it takes to update the container. This means that sometimes "devel" in `Bioconductor/bioconductor_docker` is actually referring to the current "release" version of Bioconductor (i.e. the previous Bioc version's "devel"). For further details, see this [Issue](https://github.com/Bioconductor/bioconductor_docker/issues/37), and the [Bioconductor release schedule](https://www.bioconductor.org/about/release-announcements/).  
- [`scFlow`](https://github.com/combiz/scFlow): The `rworkflows` Dockerfile template was partly adapted from the [scFlow Dockerfile](https://github.com/combiz/scFlow/blob/master/Dockerfile). Unlike other Dockerfiles, this one does not require any manual editing when applying to different R packages. This means that users who are unfamiliar with **Docker** do not have to troubleshoot making this file correctly. It also means that it will continue to work  even if your R package dependencies change. 
- [`act`](https://github.com/nektos/act): A very useful command line tool for testing **GitHub Actions** locally. 
- [`actions/runner-images`](https://github.com/actions/runner-images): Runner images for each OS provided by GitHub.  
- [`actions/setup-miniconda`](https://github.com/marketplace/actions/setup-miniconda): GitHub Action to setup Miniconda and conda environments.

## ℹ Session Info  

<details>

```{r}
utils::sessionInfo()
```

</details>

