---
title: "Bioconductor" 
author: "<h4>Authors: <i>`r auths <- eval(parse(text = gsub('person','c',read.dcf('../DESCRIPTION', fields = 'Authors@R'))));paste(auths[names(auths)=='given'],auths[names(auths)=='family'], collapse = ', ')`</i></h4>" 
date: "<h4>Vignette updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{Bioconductor} 
    %\usepackage[utf8]{inputenc}
    %\VignetteEngine{knitr::rmarkdown}
---


```{r, echo=FALSE, include=FALSE}
pkg <- read.dcf("../DESCRIPTION", fields = "Package")[1]
library(pkg, character.only = TRUE)
```

```R
library(`r pkg`)
```

# Branch-specific workflows

It may be desirable to set up multiple workflow files within the same repository.
A common use case for this is for `Bioconductor` packages, 
which rely on version-controlled
[release schedules](https://www.bioconductor.org/about/).

Because of the release schedule, you may want to have different 
virtual machine (VM) setups for each version of your package 
(which are stored on different branches of the same GitHub repository).

## `devel` branch

Only use the `devel` version of Bioc when launching 
GitHub Actions from the `devel` branch.

```{r}
v <- "devel"
f1 <- use_workflow(name = paste("rworkflows",v,sep="."), 
                   branches = v, 
                   runners = construct_runners(bioc = v), 
                   preview = TRUE,
                   force_new = TRUE,
                   save_dir = tempdir() # For demo only, use default in practice
                   ) 
```

## `RELEASE_3_17` branch

Only use the `3.17` release version of Bioc when launching 
GitHub Actions from the `RELEASE_3_17` branch.

```{r}
v <- "RELEASE_3_17"
f2 <- use_workflow(name = paste("rworkflows",v,sep="."), 
                   branches = v, 
                   runners = construct_runners(bioc = v), 
                   preview = TRUE,
                   force_new = TRUE,
                   save_dir = tempdir() # For demo only, use default in practice
                   ) 
```

## `RELEASE_*` branches

Only use the latest `release` version of Bioc when launching 
GitHub Actions from any `RELEASE_*` branch.

```r
v <- "RELEASE_*"
f3 <- use_workflow(name = paste("rworkflows",v,sep="."), 
                   branches = v, 
                   runners = construct_runners(bioc = v), 
                   preview = TRUE,
                   force_new = TRUE,
                   save_dir = tempdir() # For demo only, use default in practice
                   ) 
```

# Session Info 

<details> 

```{r Session Info}
utils::sessionInfo()
```

</details>  

<hr>
