---
title: "Dependency graph" 
author: "<h4>Authors: <i>`r auths <- eval(parse(text = gsub('person','c',read.dcf('../DESCRIPTION', fields = 'Authors@R'))));paste(auths[names(auths)=='given'],auths[names(auths)=='family'], collapse = ', ')`</i></h4>" 
date: "<h4>Vignette updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{depgraph} 
    %\usepackage[utf8]{inputenc}
    %\VignetteEngine{knitr::rmarkdown}
---


```{r}
requireNamespace("htmltools")
library(data.table)
```


A dependency graph for all GitHub repos that use the `rworkflows` GitHub Action.

# Create

Here is the code for creating the plot.

## Install required packages

```R 
if(!require("echodeps"))remotes::install_github("RajLabMSSM/echodeps",
                                                dependencies = TRUE)
```

## Create graph 

```R
res <- echodeps::dep_graph(pkg = "rworkflows",
                           method = "github",
                           shape = "hexagon",
                           exclude = c("neurogenomics_rworkflows",
                                       "neurogenomics_r_workflows"),
                           node_size = "clones_uniques",
                           reverse = TRUE,
                           save_path = here::here("reports","rworkflows_depgraph.html"))
```
 
## Save data

```R
dgc_out$metadata

saveRDS(res, here::here("reports","dgc_out.rds"))
```

## Count stars/clones/views

```R
cols <- c("stargazers_count",
          "clones_count","clones_uniques","indirect_clones_uniques",
          "views_count","views_uniques","indirect_views_uniques",
          "total_downloads","indirect_total_downloads",
          echogithub::r_repos_opts())
cols <- cols[cols %in% names(res$metadata)]

metadata_counts <- data.frame(
  total=res$metadata[repo!="rworkflows",
                         lapply(.SD, sum, na.rm=TRUE),
                         .SDcols=cols] |> t()
  )
metadata_counts
```

# Show

Hover over each node to show additional metadata.

```{r fig.height=20, fig.width=20}
htmltools::includeHTML("https://github.com/neurogenomics/rworkflows/raw/master/reports/rworkflows_depgraph.html")
```

# Identify high-impact packages

Identify the CRAN/Bioc R packages with the most number of downloads.
This guides which packages would be the most useful
to focus on implementing `rworkflows` in.

```R
pkgs <- echogithub::r_repos_downloads(which = c("CRAN","Bioc"),
                                      nThread = 10)

pkgs <- pkgs[!is.na(downloads),] 
data.table::setkeyv(pkgs,c("r_repo","downloads"))
pkgs_top <- pkgs[, tail(.SD, 10), by="r_repo"] 
methods::show(pkgs_top)
```

# Session Info 

<details> 

```{r Session Info}
utils::sessionInfo()
```

</details>  

<br>
