---
title: "Repositories analysis" 
author: "<h4>Authors: <i>`r auths <- eval(parse(text = gsub('person','c',read.dcf('../DESCRIPTION', fields = 'Authors@R'))));paste(auths[names(auths)=='given'],auths[names(auths)=='family'], collapse = ', ')`</i></h4>" 
date: "<h4>Vignette updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{Repositories analysis} 
    %\usepackage[utf8]{inputenc}
    %\VignetteEngine{knitr::rmarkdown}
---

# Install required packages

```R
for(p in c("UpSetR","githubinstall","rvest","ggplot2","data.table")){
  requireNamespace(p)
  install.packages(p)
}
```
```R
library(data.table)
```

 

# Get all packages per repo

## Base R

```{r}
baser <- rownames(installed.packages(priority="base"))
```


## CRAN

```{r} 
cran <- utils::available.packages(contriburl = "https://cran.rstudio.com/src/contrib") |> data.frame()
length(cran$Package)
```

## Bioc

*Note*: This only retrieves Bioc packages in the currently installed 
release of Bioconductor. Packages that are only in older versions of Bioc 
(and were later deprecated) will not be listed here.

```{r}
### This function gives all packages, including CRAN, Bioc, and anything currently installed. ####
# bioc <- BiocManager::available() 

### This only gives Bioc packages ####
repos <- BiocManager::repositories()
repos <- repos[names(repos)!="CRAN"]
bioc <- utils::available.packages(repos = repos) |> data.frame()
length(bioc$Package)
```

## rOpenSci

```{r}
ropensci <- 
  rvest::read_html("https://docs.ropensci.org/") |>
  rvest::html_element("#repolist") |>
  rvest::html_children() |> 
  rvest::html_text()
length(ropensci)
```

## GitHub

> The githubinstall package uses Gepuro Task Views for getting the list of R packages on GitHub. Gepuro Task Views is crawling the GitHub and updates information every day. The package downloads the list of R packages from Gepuro Task Views each time it was loaded. Thus, you can always use the newest list of packages on a new R session.
However, you may use an R session for a long time. In such case, gh_update_package_list() is useful.
gh_update_package_list() updates the downloaded list of the R packages explicitly.

However this is not actually true, 
as the file has not been updated since February 3rd 2018:
https://github.com/hoxo-m/githubinstall/issues/41

A Pull Request was made in 2019 but it was never integrated:
https://github.com/pabter/gepuro-task-views-copy/tree/76b7c4e48a704927432f328c6f898cbac0c5731c

```{r}
githubinstall::gh_update_package_list()
github <- githubinstall::gh_list_packages()
length(github$package_name)
```

## Merge all repos

```{r}
pkgs <- rbind(
  cbind(package=baser,
        repo="base"),
  cbind(package=cran$Package,
        repo="CRAN"),
  cbind(package=bioc$Package,
        repo="Bioc"),
  cbind(package=ropensci,
        repo="rOpenSci"),
  cbind(package=github$package_name,
        repo="GitHub")
  ) |>
  data.table::data.table()
pkgs_count <- pkgs[, .(count = .N), by = repo]
pkgs_count
```


## Plot

### Upset plot

```{r}
#### Create data ####
upsetr_data <- lapply(stats::setNames(unique(pkgs$repo),
                                      unique(pkgs$repo)),
                    function(r){
                      unique(subset(pkgs,repo==r)$package)
                    }) |> UpSetR::fromList()

#### Plot ####
upset_plot <- UpSetR::upset(data = upsetr_data,  
                            sets.bar.color = "slategrey",
                            main.bar.color = "slategrey",
                            text.scale = 1.5,
                            queries = list(list(query = UpSetR::intersects, 
                                                params = list("GitHub"),
                                                color = "darkred", 
                                                active = TRUE))
                            )
#### Save  ####
path <- "~/Downloads/upsetr" ##tempfile(fileext = "")
## PDF
grDevices::pdf(paste0(path,".pdf"))
upset_plot
grDevices::dev.off() 
## PNG
grDevices::png(paste0(path,".png"))
upset_plot
grDevices::dev.off() 
```

### Compute percentages

```{r}
stats_1repo <- colSums(upsetr_data[rowSums(upsetr_data)==1,])
stats_repo <- data.table::data.table(
  repo=names(stats_1repo),
  total=length(unique(pkgs$package)),
  count_all=colSums(upsetr_data),
  count_exclusive=stats_1repo
  )[,percent_all:=(count_all/total*100)][,percent_exclusive:=(count_exclusive/total*100)]
stats_repo
```

# Session Info 

<details> 

```{r Session Info}
utils::sessionInfo()
```

</details>  

<br>
