---
title: "Get Started" 
author: "<h4>Authors: <i>`r auths <- eval(parse(text = gsub('person','c',read.dcf('../DESCRIPTION', fields = 'Authors@R'))));paste(auths[names(auths)=='given'],auths[names(auths)=='family'], collapse = ', ')`</i></h4>" 
date: "<h4>Vignette updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{rworkflows} 
    %\usepackage[utf8]{inputenc}
    %\VignetteEngine{knitr::rmarkdown}
---


```{r, echo=FALSE, include=FALSE}
pkg <- read.dcf("../DESCRIPTION", fields = "Package")[1]
library(pkg, character.only = TRUE)
```


```R
library(`r pkg`)
```

# `use_workflow`

User only have to run `use_workflow` once per R package to create
a workflow file that calls the `rworkflows` action. 

```{r}
workflow <- rworkflows::use_workflow(run_bioccheck = FALSE, 
                                     run_rcmdcheck = TRUE,  
                                     run_pkgdown = TRUE, 
                                     run_docker = TRUE,
                                     docker_user = "bschilder",
                                     docker_org = "neurogenomicslab")
```

# `use_badges`

This function creates a banner containing badges, a hex sticker (if one is available), and author names.

```{r, results='asis'}
badges <- rworkflows::use_badges()
```


# `use_dockerfile`

Create a *Dockerfile* that installs your R package and all its 
*Imports*/*Suggests*. It is normally not necessary for users to run this function themselves unless they would like to use it to create a template *Dockerfile* and then customise it further (rather than creating one on the fly).

```{r, results='asis'}
dockerfile <- rworkflows::use_dockerfile(save_dir = tempdir())
```

# Session Info 

<details> 

```{r Session Info}
utils::sessionInfo()
```

</details>  

<br>
