---
title: "Getting Started" 
author: "<h4>Authors: <i>`r auths <- eval(parse(text = gsub('person','c',read.dcf('../DESCRIPTION', fields = 'Authors@R'))));paste(auths[names(auths)=='given'],auths[names(auths)=='family'], collapse = ', ')`</i></h4>" 
date: "<h4>Vignette updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{templateR} 
    %\usepackage[utf8]{inputenc}
    %\VignetteEngine{knitr::rmarkdown}
---


```{r, echo=FALSE, include=FALSE}
pkg <- read.dcf("../DESCRIPTION", fields = "Package")[1]
library(pkg, character.only = TRUE)
```


```R
library(`r pkg`)
```

# Examples 

### 1. Create your R package

If you haven't already [created your R package](https://support.rstudio.com/hc/en-us/articles/200486488-Developing-Packages-with-the-RStudio-IDE), 
you can use [`templateR`](https://github.com/neurogenomics/templateR) as a CRAN/Bioconductor-ready template.

### 2. Setup GitHub Secrets 

GitHub now lets you store "Secrets" within each repo. 
These are basically hidden variables that no one but the repo admins 
can see/edit. 

See here for instructions on how to create [GitHub Secrets](https://docs.github.com/en/codespaces/managing-codespaces-for-your-organization/managing-encrypted-secrets-for-your-repository-and-organization-for-github-codespaces) 
and [GitHub Organization Secrets](https://docs.github.com/en/codespaces/managing-codespaces-for-your-organization/managing-encrypted-secrets-for-your-repository-and-organization-for-github-codespaces#adding-secrets-for-an-organization). 

You will need to store the following variables as Secrets in your GitHub repo.

* `PAT_GITHUB`: <Your GitHub Personal Authentication Token 
generated [via the following instructions](https://docs.github.com/en/authentication/keeping-your-account-and-data-secure/creating-a-personal-access-token)>   
* `DOCKER_TOKEN`: <Your DockerHub access token generated 
[via the following instructions](https://docs.docker.com/docker-hub/access-tokens/)>   

### 3. Create workflow file 

`rworkflows` is also an R package that contains helper functions for setting up
GHA workflows in your R package directory. 

```R
if(!require("rworkflows")) remotes::install_github("neurogenomics/rworkflows")
path <- rworkflows::use_workflow()
```   

### 4. Push to GitHub

Now, these workflows will automatically be run every time you push changes
to your GitHub repo.  

```
git add .
git commit -m "Added GHA workflow via rworkflows::use_workflow()"
git push
```

You can then monitor the progress and view the results of your workflows 
via the *"Actions"* tab of your GitHub repo. 

**NOTE**: If you do not see an *"Actions"* tab, go to *Settings --> Actions* and
make sure "Actions permissions" is activated. 


# Session Info 

<details> 

```{r Session Info}
utils::sessionInfo()
```

</details>  

<br>
