---
title: "Get Started" 
author: "<h4>Authors: <i>`r auths <- eval(parse(text = gsub('person','c',read.dcf('../DESCRIPTION', fields = 'Authors@R'))));paste(auths[names(auths)=='given'],auths[names(auths)=='family'], collapse = ', ')`</i></h4>"
date: "<h4>Vignette updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{rworkflows} 
    %\usepackage[utf8]{inputenc}
    %\VignetteEngine{knitr::rmarkdown}
---


```{r, echo=FALSE, include=FALSE}
pkg <- read.dcf("../DESCRIPTION", fields = "Package")[1]
library(pkg, character.only = TRUE)
```

```R
library(`r pkg`)
```

# GitHub Secrets 

Before pushing changes to your new R package, you may want to set up one or more
[GitHub Secrets](https://docs.github.com/en/actions/security-guides/encrypted-secrets):

* `GITHUB_TOKEN` [Optional]: Can grant access to private
    repos on GitHub Actions. You can generate your very own Personal
    Authentication Token using [these
    instructions](https://docs.github.com/en/authentication/keeping-your-account-and-data-secure/creating-a-personal-access-token).   
* `DOCKER_TOKEN` [Optional]: Allows GitHub Actions to push to a
    [DockerHub](https://hub.docker.com) account. 

# `use_workflow`

## dynamic action

User only have to run `use_workflow` once per R package to create
a workflow file that calls the `rworkflows` action. 

```{r}
workflow <- rworkflows::use_workflow(run_bioccheck = FALSE, 
                                     run_rcmdcheck = TRUE,  
                                     run_pkgdown = TRUE, 
                                     run_docker = TRUE,
                                     docker_user = "bschilder",
                                     docker_org = "neurogenomicslab",
                                     ## Use default save_dir in practice
                                     save_dir = tempdir())
```

## static workflow

Alternatively, you may use 

```{r}
workflow_static <- rworkflows::use_workflow(name = "rworkflows_static",
                                     run_bioccheck = FALSE, 
                                     run_rcmdcheck = TRUE,  
                                     run_pkgdown = TRUE, 
                                     run_docker = TRUE,
                                     docker_user = "bschilder",
                                     docker_org = "neurogenomicslab",
                                     ## Use default save_dir in practice
                                     save_dir = tempdir())
```

# `use_badges`

This function creates a banner containing badges, 
a hex sticker (if one is available), and author names.

```{r, results='asis'}
badges <- rworkflows::use_badges()
```


# `use_dockerfile`

Create a *Dockerfile* that installs your R package and all its 
*Imports*/*Suggests*. It is normally not necessary for users to run this function themselves unless they would like to use it to create a template *Dockerfile* and then customise it further (rather than creating one on the fly).

```{r, results='asis'}
## Use default save_dir in practice
dockerfile <- rworkflows::use_dockerfile(save_dir = tempdir()) 
```

# Templates

You can generate templates for each of the following R package elements.
These templates are designed to dynamically autofill as as much information 
as possible (package name, date, authors) to minimise manual editing steps and
ensure documentation is as up-to-date as possible.

## README

README rmarkdown file. 
Allows you to run code inside to generate a README *markdown* file. 

```{r}
## Use default save_dir in practice
readme <- rworkflows::use_readme(save_dir = tempdir())
```

## Vignette: Get started

Generate a vignette on how to get started with your R package.
Requires additional editing to fill in examples.

```{r}
## Use default save_dir in practice
vignette1 <- rworkflows::use_vignette_getstarted(package = "mypackage",
                                                 save_dir = tempdir())
```


## Vignette: docker

Generate a vignette on how to install your R package via with your R package, 
RStudio, and all dependencies already installed.
This vignette does not require any manual editing after creation (unless you 
want to change things like port number, for example).

Note, this is only relevant when you have a Dockerhub repo for your R package,
e.g. created with:

```R
rworkflows::use_workflow(run_docker = TRUE, 
                         docker_org = "<docker_org>")
```

```{r}
## Use default save_dir in practice
vignette2 <- rworkflows::use_vignette_docker(docker_org = "neurogenomicslab",
                                             save_dir = tempdir())
```

# Session Info 

<details> 

```{r Session Info}
utils::sessionInfo()
```

</details>  

<hr>
